%!TEX

\title{Cover Letter}
\maketitle

%\noindent\textsc{To:}\\
\toaddress
    {Anthropology Collections}
    {Field Museum of Natural History}
    {1400 S. Lake Shore Dr.}
    {Chicago}
    {IL}
    {60605}
    {United States}

I would like to express interest in your job opening for a Collections Assistant in the Anthropology
Collections. As a current Senior in Anthropology at the University of Illinois with strong research
and cataloging skills, I believe I can be a welcome candidate for this position.

Studying Anthropology at a research university has given me practical
training for professional work in the museum setting. Working with the Department of Anthropology's
fragile collection of primate bones and artifacts has helped me to understand how to ensure such
materials persist for study by generations of students rather than crumble to dust. My studies have
also included a large focus on the ethics and practice of repatriation, including both NAGPRA
and efforts to return objects across national borders, a skill that squares well with the museum's
request for candidates' being able to relate with descendant communities and tribal groups.

Working at the campus art museum, I learned how to help members of the public enjoy their
experiences spending time at the wonderful public galleries present.
Although my term at the museum did not include any curatorial training or hands-on collections
work, I was able to learn a great deal from my position as an envoy between the public and the
educators who performed much of the behind-the-scenes work. Because the museum houses many
academics of various fields, I enjoyed my ability to delegate curious visitors' questions to
relevant curators, bridging the divide between the public's static experience of a museum
collection and the research work that drives the museum.

I can also say that I have exceptional technical skills managing databases and computerized information.
I have several years of experience working with software, including contributions to free software
projects as well as professional work developing bespoke applications and Microsoft Office
documents. While I do not have experience with KE EMu, I can rapidly gain proficiency with new
database management suites.

\signature