\title{Cover Letter}

%\begin{document}
\maketitle

%\noindent\textsc{To:}\\
\toaddress
    {Michael Martin\\Research Coordinator}
    {Cline Center for Advanced Social Research}
    {207 Strata Building, M/C 689}
    {Champaign}
    {IL}
    {61820}
    {United States}

I would like to express interest in your job opening for an analyst in civil
unrest (virtual job board position~43808). As a current Senior in Anthropology at the
University of Illinois with strong skills in research, writing, and data manipulation,
I believe I can be a welcome candidate for this position.

I have long been an avid yet critical consumer of the news media, and my analytic and
reading skills are thus honed well towards the requirements outlined in the job description.
I felt drawn to this specific advertisement as I am currently reading \emph{Manufacturing
Consent} by Herman \& Chomsky, of which I have particularly enjoyed the quantitative
analysis of news reporting and its sociological conditions. I believe that my understanding
of historical context and ability to apply it to current events is also well-formed and
will apply well to my work.

My studies in anthropology have given me a diverse array of formal independent research experiences.
Although my work observing the behavior of wild \emph{Cebus capucinus} monkeys is not
directly applicable to this job, I have researched the lives of persons with
disabilities in Kenya, where civil unrest and terrorism from groups such as al-Shabaab
is a far more pressing part of daily life. With such a firsthand understanding of how
people experience poverty in developing countries, my ability to understand local
peoples' relations to civil unrest. To the extent that it may be required, I do have a
novice-to-intermediate understanding of the Swahili language and can process local news
reports on East Africa.

Regarding your desire for a candidate with skills in data collection and content analysis,
I have previously performed text-based analysis on NCBI PubMed abstracts for a term
paper\footnotemark\@. Although it is primarily self-taught, I consider myself having
intermediate proficiency in quantitative content analysis. I am sure that my skills
in this area will benefit my work in the Cline Center.

\footnotetext{Archived at \url{https://archive.danleonard.us/scholarship/coursework/illinois/ANTH/438/microbiome.xhtml}}

\signature

%\end{document}