\title{Cover Letter}

\begin{document}
\maketitle

%\noindent\textsc{To:}\\
\toaddress
    {Army Applicant Help Desk}
    {KC-APF-W2ST01}
    {U.S. Army Engineer District}
    {Los Angeles}
    {CA}
    {}
    {United States}

I would like to express interest in your job posting for a 0401 Biologist at the Army
Corps of Engineers (announcement WTKC190273435215HS, recent graduate pathway). I am
currently in my final year studying Biological Anthropology and Integrative Biology at
the University of Illinois at Urbana-Champaign, and am now exploring ways to take this
education into practical use. My combination of skills from both
biology and anthropology makes me an exceptional fit in qualifying for this position.

I have research experience in bioscience fieldwork, having spent several weeks on an
independent research project in Costa Rica on \textit{Cebus capucinus} ecology and
behavior. In working on this project, I gained data analytics skills which I can
readily employ towards this position's need for biological survey data evaluation.

As an anthropology student, I gained the skills to work with many groups of people.
My research work has taken me to rural Kenya, where I worked with nongovernmental
organizations and their stakeholders, exploring how local, national, and
international policies affected groups of persons with disabilities. Anthropology,
as both a science and a member of the humanities, allows me to readily manage contacts
and coordinate others in the practice of scientific work, a major part of this hiring
announcement.

Throughout this work, I have been a driven researcher and writer. While I have not
had experience creating records of decision \textit{per se}, my experience 
composing formal research documents is readily adaptable to preparing concise, formal
documents.

I hope you are able to find that my skills are well-attuned to this position.

\signature

\end{document}