\title{Cover Letter}

\maketitle

%\noindent\textsc{To:}\\
\toaddress
    {Critical Care Decontamination System}
    {Battelle Memorial Institute}
    {}
    {Chicago}
    {IL}
    {}
    {United States}

I would like to express my interest in your recruitment of a
CCDS Decontamination Technician for the current COVID-19 crisis.
As a student on the cusp of graduation at the University of
Illinois with expertise in research and protocols, I am
certain I can be a welcome candidate for this vital role.

In my undergraduate career, I have been taken part in and orchestrated
several research projects. In this formal research work I have demonstrated
great aptitude for data management and following standardized processes,
critical skills for tracking inventories and decontaminating PPE.
% Studying the field of Anthropology has given me research skills that
% are particularly attuned to the requirements of \@employer's needs.
% The discipline is heavily focused on understanding peoples of disparate
% backgrounds and cultures, which influences not only my work but my worldview and
% ideology. As a student of Anthropology, I have spent extended time in different
% cultures in addition to my studies. My studies also include great
% experience in both qualitative and quantitative data interpretation: in 2017
% I conducted an independent research project collecting data on wild
% capuchin monkeys for several weeks, performing statistical hypothesis
% tests on the data I collected; in 2018, I spent a semester in Kenya, where
% I surveyed a population of persons with disabilities and collected qualitative
% data on their life experiences. My most recent project involved a comprehensive
% and quantitative literature review on published ecological data.
As a function of this research experience, I have also displayed exceptional
communication and writing skills. For all of my undergraduate research projects,
I developed presentations, including posters and slideshows, focused both for
colleagues and laypersons. Should it be necessary to report to stakeholders
such as hospitals or government, I can be an asset to Battelle.
% In my past employment, I have displayed significant
% diligence and attention to detail in applying this communication skill. At
% Gold Rush Gaming in the past summer, I created reports for the marketing department
% and designed document templates for regular use in public relations and
% in internal communication.
% At the University Library, I helped scholars
% find academic sources for their research in one of the country's largest
% library systems.

As this role is primarily laborious in nature, I can commit to my physical
readiness for the role. Although the current crisis has interrupted trips to
the gym, I can certainly meet the stated requirement of regularly
lifting fifty pounds of equipment as part of my daily work, even while clothed
in PPE. I also do not suffer from any medical issues that would place me at
elevated risk for COVID-19.

Finally, I also have a passionate interest in assisting the decontamination
effort of Battelle. I am very willing to relocate and work diligently as my
contribution towards the Institute's efforts. I can assure all involved
partners that my work in this crisis will be performed with the utmost caution
and respect for the fact that many thousands of lives are on the line.

I hope you find my skills and experience are well-attuned to be
a welcome contribution to the fight against SARS-CoV-2.

\signature