\title{Cover Letter}

\begin{document}
\maketitle

%\noindent\textsc{To:}\\
\toaddress
    {Aquatic Capital Management}
    {}
    {1 North Wacker Drive, Ste. 850}
    {Chicago}
    {IL}
    {60606}
    {United States}

I would like to express interest in your job opening for a Quantitative Research Intern.
As a current Senior in Anthropology at the University of Illinois with strong research
and data manipulation skills, I believe I can be a welcome candidate for this position.

Studying at a research university has given me practical experience
in analyzing data to make models and predictions. Through my academic career I have
conducted both quantitative and qualitative research with a diverse array of peers and
advisors.
My interdisciplinary social science background ensures that this analytical skill is
coupled with a holistic understanding, never losing sight of the larger picture of how
social structures and less-quantitative aspects of society can affect my research targets.
This is especially important in the analysis of financial markets, where the
anthropological aspect of the economy can give insights to complement sheer numerical
performance.

Along with my social science research skills, I have experience in software development
and database management, including contributions to free software
projects as well as professional work developing bespoke userspace applications. I derive
enjoyment in solving complex problems, and would be honored to bring these skills to Aquatic.
%and Microsoft Office documents
\signature

\end{document}