\title{Cover Letter}

\maketitle

%\noindent\textsc{To:}\\
\toaddress
    {}
    {Truth Initiative}
    {}
    {Washington}
    {DC}
    {20001}
    {United States}
    
I would like to express interest in your recruitment of a research
assistant. As a current Senior in Anthropology at the University of
Illinois with strong research and data manipulation skills, I am
certain I can be a welcome candidate for this position.

Studying the field of Anthropology has given me research skills that
are particularly attuned to the requirements of Truth Initiative's needs.
I have experience in both qualitative and quantitative data interpretation:
I conducted an independent research project collecting data on wild
capuchin monkeys for several weeks, performing statistical hypothesis
tests on the data I collected; later, I spent a semester in Kenya, where
I surveyed a population of persons with disabilities and collected qualitative
data on their life experiences. My most recent project involved a comprehensive
and quantitative literature review on published ecological data.

As a function of this research experience, I have displayed exceptional
communication and writing skills. For all of my undergraduate research projects,
I developed presentations, including posters and slideshows, focused both for
colleagues and laypersons. In my past employment, I have displayed significant
diligence and attention to detail in applying this communication skill. At
Gold Rush Gaming in the past summer, I created reports for the marketing department
and designed document templates for regular use in public relations and
in internal communication. At the University Library, I helped scholars
find academic sources for their research in one of the country's largest
library systems.

My qualification for this position extends beyond my particular skill set -- I
also have an passionate interest in working for Truth Initiative. Ending tobacco
and nicotine use is important to me, and I wish to work on the front lines of
this challenge. Having spent time performing qualitative ethnographic
research in a developing nation, I bring a comparative view of tobacco use across
cultural and economic divides. Further, my studies have been concurrent with the
shocking rise in e-cigarette use amongst teens and students. I find the new vaping
trends disturbing and hope to be able to prevent a new generation of nicotine
addicts.

I hope you are able to find that my skills and drive are well-attuned to this position.

\signature