\title{Cover Letter}

\maketitle

%\noindent\textsc{To:}\\
\toaddress
    {Consortium on School Research}
    {University of Chicago}
    {1313 E.\ 60\textsuperscript{th}\ Street}
    {Chicago}
    {IL}
    {60637}
    {United States}

I would like to express my interest in your recruitment of a
Research Analyst~\RN{1} with a social science degree graduating
by this June.
% I would like to express interest in your recruitment of a research
% assistant.
As a current Senior in Anthropology at the University of
Illinois with strong research and data manipulation skills, I am
certain I can be a welcome candidate for this position.

Studying the field of Anthropology has given me research skills that
are particularly attuned to the needs of the Consortium.
I have experience in both qualitative and quantitative data interpretation:
I conducted an independent research project collecting data on wild
capuchin monkeys for several weeks, performing statistical hypothesis
tests on the data I collected; later, I spent a semester in Kenya, where
I surveyed a population of persons with disabilities and collected qualitative
data on their life experiences. My most recent project involved a comprehensive
and quantitative literature review on published ecological data.

As a function of this research experience, I have displayed exceptional
communication and writing skills. For all of my undergraduate research projects,
I developed presentations, including posters and slideshows, focused both for
colleagues and laypersons. In discussions with the Consortium's researchers
and stakeholders, I can present findings and provide feedback to others' work.
% In my past employment, I have displayed significant
% diligence and attention to detail in applying this communication skill. At
% Gold Rush Gaming in the past summer, I created reports for the marketing department
% and designed document templates for regular use in public relations and
% in internal communication.
% At the University Library, I helped scholars
% find academic sources for their research in one of the country's largest
% library systems.

In the areas of statistical programming, I have experience in the use of both
R and Python for data science, along with an adept ability to learn new tools
such as SAS or STATA as needed. I enjoy thinking within the context of statistical
analysis, identifying correlations and building models around complex datasets.

Finally, I also have a passionate interest in improving the lives of students.
I attended public school throughout my life, presently culminating in a public
university in my home state. As the educational system is deeply intertwined
with nearly all facets of urban life, I consider it vitally important to
assist the Consortium in informing the practice of Chicago's public schools.
As the Consortium's next research agenda develops, I hope to contribute to
its future direction and look toward improving educational outcomes.

I hope you find my skills and experience are well-attuned to be
a welcome contribution to the Consortium.

\signature